Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-19 documents/mixtures/mixture_models.tex
punctuation

Gaussians are remarkable distribution functions.  They have the
incredible properties that---in any number of dimensions---the
convolution (or correlation) of one multivariate Gaussian with another
is itself a multivariate Gaussian, and any product of multivariate
Gaussians is itself a multivariate Gaussian but with a different
normalization.  Furthermore, the means and variance tensors of the
Gaussians output by these operations are related simply to the means
and variance tensors of the inputs.  Add to these wonders the fact
that Gaussians form a complete basis for representing (smooth)
probability distribution functions and it becomes remarkable that we
don't do everything we do in terms of Gaussians.

@@

We are not the first in this space deconvolution and modeling of
galaxy images with mixtures of Gaussians has been done very
successfully before (for example, \citealt{bendinelli, emsellem,
  bendinelli2, cappellari}).  However, the idea behind those projects
was to use the mixture of Gaussians to provide a very free form for
the isophotes or morphologies of resolved galaxies or other complex
scenes.  Here our goals are very limited: We want to improve the
performance of standard galaxy image model fitting by expressing the
standard galaxy models---the exponential and de~Vaucouleurs
profiles---as rigid mixtures of Gaussians.

>>>>

\noindent
Gaussians are remarkable distribution functions.  They have the
incredible properties that---in any number of dimensions---the
convolution (or correlation) of one multivariate Gaussian with another
is itself a multivariate Gaussian, and any product of multivariate
Gaussians is itself a multivariate Gaussian but with a different
normalization.  Furthermore, the means and variance tensors of the
Gaussians output by these operations are related simply to the means
and variance tensors of the inputs.  Add to these wonders the fact
that Gaussians form a complete basis for representing (smooth)
probability distribution functions and it becomes remarkable that we
don't do everything we do in terms of Gaussians.

@@

We are not the first in this space:  Deconvolution and modeling of
galaxy images with mixtures of Gaussians has been done very
successfully before (for example, \citealt{bendinelli, emsellem,
  bendinelli2, cappellari}).  However, the idea behind those projects
was to use the mixture of Gaussians to provide a very free form for
the isophotes or morphologies of resolved galaxies or other complex
scenes.  Here our goals are very limited: We want to improve the
performance of standard galaxy image model fitting by expressing the
standard galaxy models---the exponential and de~Vaucouleurs
profiles---as rigid mixtures of Gaussians.
